Refinements for open automata

### 2022-06-10 2021-Refinement/paper/refinementarticle.tex
first draft exalanation

%\subsection{Deadlock Reduction, Reachability, and Composition}
\TODO{rewrite}
A notion that is often used in the context of refinement is the notion of deadlock reduction. This property considers that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too. This notion is not much interesting in the general case as there is a priori no relation between the two transitions. However, when the relation that relates states is a simulation, this will relate the possible transitions and the deadlock reduction will become a valuable property.
%
%Next definition states that if $T_2$ is not in a deadlock position then $T_1$ can do a transition but not necessarily with the same input values. This is very weak but sufficient when composed with the def  of simulation.

@@

\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\big(
 \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\\
 \land \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
 \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^2_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
 R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2}\big)
\wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}
\end{multline*}
Finally , because $R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\mpar{
 \alpha_{13}=\alpha_{1 3x} \land
J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
 R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
\end{multline*}

>>>>

%\subsection{Deadlock Reduction, Reachability, and Composition}
\TODO{rewrite}
A notion that is often used in the context of refinement is the notion of deadlock reduction. The objective i that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too. 
What raises this difficulty is the fact that the automaton that simulates a specification features any behaviour that contains the behaviour of the specification but this is only verified at each state of the automaton. In this definition, nothing prevents the implementation from adding non-determinism and non-deterministically reaching a deadlock that does not exist in the specification.  
The idea is that simulation states that there is a relation between states such that, for related states, the behaviour of the implementation must follow the behaviour of the specification ... but also when both the implementation and the specification do the same transition, they stay related.
This ensures a form of continuity in the comparison in the sense that the refined system is constrained to follow the behaviour of the simulated system along a given scenario. 
In terms of traces this amounts to some form of deadlock reduction: for each trace followed by the simulated system if the refined system followed the beginning of the trace, it must be able to keep following the trace. Except that the notion of trace is insufficient to characterize a scenario of execution in OAs because of the presence of guards, states, and holes.

%
%Next definition states that if $T_2$ is not in a deadlock position then $T_1$ can do a transition but not necessarily with the same input values. This is very weak but sufficient when composed with the def  of simulation.

@@

\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\big(
 \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\\
 \land \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
 \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^2_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
 R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2}\big)
\wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}
\end{multline*}
Finally , because $R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
\bigwedge_{x\in X}
\mpar{
 \alpha_{13}=\alpha_{1 3x} \land
J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
 R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
\end{multline*}
